Multiple quantum NMR in solids as a method of a determination of Wigner--Yanase skew information

### 2021-02-19 manuscript.tex
Fix typos

The analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{23}.
In Fig.~\ref{fig:3} the close results on the many--spin entanglement for both used informations for the system consisting of $6\div 12$ spins is presented.~\cite{15}.

>>>>

The analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{15,23}.
In Fig.~\ref{fig:3} the close results on the many--spin entanglement are presented for the system consisting of six spins at different temperatures for both used informations.
